\documentclass[10pt,a4paper,helvetica]{moderncv}

\moderncvtheme[red]{classic}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\firstname{Toan}
\familyname{Phung}
\address{Unit 30, 1-3 Harrys Rd}{4068 Taringa}
\mobile{0497043505}
\email{toan.phung@uq.net.au}
\homepage{https://github.com/noatgnu}

\begin{document}
\maketitle
\section{Education}
\cventry{2017--Present}{Doctor of Philosophy}{The University of Queensland}{St. Lucia, Queensland, Australia}{}{}
\cventry{2014--2016}{Master of Molecular Biology (Advanced)}{The University of Queensland}{St. Lucia, Queensland, Australia}{}{}
\cventry{2009--2014}{Bachelor of Science in Biochemistry}{The University of Montana}{Missoula, Montana, United States}{}{}
\closesection{}

\section{Relevant Experiences}
\textbf{\cvline{Research Project}{\emph{uPEPperoni: A 5' UTR Short Open Reading Frame searching tool (2016)}}}
\cvline{Supervisor}{Associate Professor Joe Rothnagel}
\cvline{Description}{A tool for searching of sORF in user's input and similar sORF in other protein sequences within the program database and visualization of their positions using heatmap.}
\cvline{Contribution}{
    Revamping code base and bug fixing.
    \newline Shifting part of the database from file based to RDBMS.
    \newline Integrating and improving functionality.}
\textbf{\cvline{Research Project}{\emph{Evolution and constraints of N-glycosylation Sequons (2017-Present)}}}
\cvline{Supervisor}{Associate Professor Benjamin L. Schulz}
\cvline{Description}{Analysis of N-glycosylation sequons in Homo sapiens glycoprotein homologs, their alignment and phylogenetic relation.}
\cvline{Contribution}{Programming of automation workflow, logic and analyses}
\textbf{\cvline{Research Project}{\emph{SWATHLib, an automated workflow for theoretical ion library generation for glycopeptides (2018)}}}
\cvline{Supervisor}{Associate Professor Benjamin L. Schulz}
\cvline{Description}{DDA based spectral library together with the complexity from post-translational modifications cannot optimally represent the ions within SWATH data. A workaround for this problem is a tedious process of creating a manually curated ion library. SWATHLib is created to address these problems.}
\cvline{Contribution}{Writing of the JavaScript front-end using Angular 7 for automated user input collection.\newline Implementing a Python back-end for processing of user requests and automated modification combination generation.}


\closesection{}
\section{Extra-Curricular Activities}
\cventry{2017}{Poster presented at the 13th Annual SCMB Research Students Symposium.}{The University of Queensland}{Australia}{}{}
\cventry{}{Queensland Mass Spectrometry Symposium 2017}{QIMR Berghofer}{Australia}{}{}
\cventry{2015}{Poster presented at the 11th Annual SCMB Research Students Symposium.}{The University of Queensland}{Australia}{}{}
\cventry{2009--2014}{International Student Association (Executive officer and Webmaster)}{The University of Montana}{United States}{}{}
\section{Skills}
\begin{cvcolumns}
    \cvcolumn{Programming Languages}{Python\newline JavaScript\newline TypeScript\newline Golang\newline R\newline \LaTeX{}}
    \cvcolumn{Data Visualization}{D3.js}
    \cvcolumn{Languages}{English\newline Vietnamese}
\end{cvcolumns}
\closesection{}
\section{Professional Membership}
\cventry{2018-Present}{Australian Bioinformatics and Computational Biology Society}{}{}{}{}
\section{References}
\begin{cvcolumns}
    \cvcolumn{Benjamin L. Schulz}{Associate Professor \\ NHMRC Career Development Fellow \\ School of Chemistry and Molecular Biosciences \\ Faculty of Science \\ The University of Queensland \\ \phonesymbol +61 7 336 54875 \\ \emailsymbol b.schulz@uq.edu.au}
    \cvcolumn{Joe Rothnagel}{Associate Professor \\ Past Chair, Teaching \& Learning Committee (2009-2013) \\ School of Chemistry and Molecular Biosciences \\ Faculty of Science \\ The University of Queensland \\ \phonesymbol +61 7 336 54629 \\ \emailsymbol j.rothnagel@uq.edu.au}
\end{cvcolumns}
\closesection{}
\clearpage
\end{document}